Characterizing Stellar Streams by ML

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

\newcommand{\package}[1]{\textsc{#1}}
\newcommand{\stream}[1]{#1}
\newcommand{\dataarchive}[1]{\texttt{#1}}
\newcommand{\Gaia}{\dataarchive{Gaia}}
\newcommand{\gaia}{\dataarchive{gaia}}

@@

        Streams have a diversity of measurement coverage: several have full 6-D
        astrometrics as well as photometrics and chemical abundances available
        \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L},
        while most have partial coverage, lacking some feature dimensions.
        % TODO: terminology ND-phase-space vs feature columns
        Most streams in \gaia {\color{red} [cite]}, for instance, have proper
        motions but not radial velocities nor reliable parallax measurements.
        Followup surveys, like \dataarchive{S5} {\color{red} [cite]}, add many
        feature dimensions, however only for a select set of streams. Given the
        diversity of coverage it is important that the likelihood model --
        \autoref{eq:membership_prob} -- account for missing data.

@@

            % TODO? expand this section.
            The last approach to the issue of the PDMF, and the one we take in
            this work, is to render it unimportant.  With fixed age,
            metallicity, and other isochrone model parameters, the primary
            purpose of the isochrone is to allow the model to determine the
            distance modulus of the stream. For this, only a portion of the
            stream need be modeled.  For streams with observable main sequence
            turn-offs, like \stream{GD-1} in \gaia, this portion of the
            isochrone has both many stars and a relatively small range in
            masses. Thus, we restrict the mass range of the isochrone such that
            we are modeling only a region of interest over which the PDMF does
            not contribute to the final result.
            % TODO? work in something to the effect of: The PDMF doesn't have an
            % enormous impact, regardless as the isochrone model is very thin
            % and stars close to the isochrone photometrically are generally
            % quite far astrometrically. This is an advantange of simultaneous
            % modeling, where errors in one model are balanced by other parts of
            % the model.

@@

        We utilize data from {\it Gaia} DR3 for the astrometric coordinates of
        each star, and Pan-STARRS1 to obtain more accurate color information. We
        adopt broad cuts on the cross-matched data to limit the field to a
        region known to contain GD-1. We perform these rough cuts by requiring
        \JN{fill in what the cuts are and reference proper motion figure and CMD
        figure.}

>>>>

\newcommand{\package}[1]{\textsc{#1}}
\newcommand{\stream}[1]{#1}
\newcommand{\dataarchive}[1]{\texttt{#1}}
\newcommand{\Gaia}{\dataarchive{Gaia}}
\newcommand{\PanStarrs}{\dataarchive{Pan-STARRS1}}

@@

        Streams have a diversity of measurement coverage: several have full 6-D
        astrometrics as well as photometrics and chemical abundances available
        \citep[e.g.,][]{Koposov2019, 2020A&A...635L...3A, 2022ApJ...928...30L},
        while most have partial coverage, lacking some feature dimensions.
        % TODO: terminology ND-phase-space vs feature columns
        Most streams in \Gaia {\color{red} [cite]}, for instance, have proper
        motions but not radial velocities nor reliable parallax measurements.
        Followup surveys, like \dataarchive{S5} {\color{red} [cite]}, add many
        feature dimensions, however only for a select set of streams. Given the
        diversity of coverage it is important that the likelihood model --
        \autoref{eq:membership_prob} -- account for missing data.

@@

            % TODO? expand this section.
            The last approach to the issue of the PDMF, and the one we take in
            this work, is to render it unimportant.  With fixed age,
            metallicity, and other isochrone model parameters, the primary
            purpose of the isochrone is to allow the model to determine the
            distance modulus of the stream. For this, only a portion of the
            stream need be modeled.  For streams with observable main sequence
            turn-offs, like \stream{GD-1} in \Gaia, this portion of the
            isochrone has both many stars and a relatively small range in
            masses. Thus, we restrict the mass range of the isochrone such that
            we are modeling only a region of interest over which the PDMF does
            not contribute to the final result.
            % TODO? work in something to the effect of: The PDMF doesn't have an
            % enormous impact, regardless as the isochrone model is very thin
            % and stars close to the isochrone photometrically are generally
            % quite far astrometrically. This is an advantange of simultaneous
            % modeling, where errors in one model are balanced by other parts of
            % the model.

@@

        We utilize data from \Gaia{} DR3 for the astrometric coordinates of
        each star, and \PanStarrs{} to obtain more accurate color information.

        We cross-match the \Gaia{} field on \PanStarrs{} using the provided
        \texttt{Best-neighbors} catalog.

        adopt broad cuts on the cross-matched data to limit the field to a
        region known to contain GD-1. We perform these rough cuts by requiring...

        We use the \texttt{GD1Koposov10} frame defined in Gala \TODO{[cite gala and Koposov10]}

        \JN{fill in what the cuts are and reference proper motion figure and CMD
        figure.}
